Contracts for unions and intersections are hard for Nickel

### 2021-05-06 paper.tex
Move existing documentation to appendices
Tentative outline

\section*{Introduction}
Intro\unsure{todo}
\info{Goals of the paper: position paper: unions/intersections nice in
theory problematic in practice. In particular non-orthogonal with the
rest of the features of your language.}
\section{Background on union types}

>>>>

\section*{Introduction}
Intro\unsure{todo}
\info{Goals of the paper: position paper: unions/intersections nice in
theory problematic in practice. In particular non-orthogonal with the
rest of the features of your language.}

\newpage

\section{Features of languages}
\info{Zoology of various features that we will eventually show
  conflict with this or that property or implementation of union and
  intersection. Including user-define contracts.}

\newpage

\section{Union \& intersection}
\info{What are they, what are they used for.}

\newpage

\section{Issues coming from the semantics}
\info{What goes wrong or difficult when trying to implement union and
  intersection literally}

\newpage

\section{Issues in concrete restrictions from the literature}
\info{The various papers and the tradeoffs they make}

\newpage

\section{Related work}
\info{Including a mention of statically typed systems with union}

\newpage

\section{Conclusion}

\appendix

\section{Background on union types}
